Microlensing as a possible probe of event-horizon structure in quasars

### 2017-09-14 paper1/ms.tex
editing remaining points

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{compare-mag.eps}
\caption{``Visiting Figure''.  Only in red/blue version, not for the paper.}
\end{figure}

@@

In addition to the source parameters, the fitting procedure includes
three nuisance parameters, namely the brightness normalisation and the
start and end points on the path.  The latter two are equivalent to
considering the location of the caustic with respect to the starting
point and the velocity component of the source transverse to the
caustic (that is, $v_p$).  The orientation of the source track is
another nuisance parameter, but we do not include it, because for a
pure fold, changing the orientation of the source track is equivalent
to changing $v_p$ and the orientation of the source (see
Figure~\ref{fig:infinite_fold}), all parameters that are included.
Since the caustic is not a perfect fold, disregarding the orientation
of the source track can be expected to introduce some systematic
error.

>>>>

\begin{figure}
\centering
  \includegraphics[width=0.5\textwidth]{compare-mag.eps}
\caption{[{\bf Temporary.} This figure is included only the in
    red/blue version, and is not for the paper.] Overlay from the
  three preceding figures.}
\end{figure}

@@

In addition to the source parameters, the fitting procedure includes
three nuisance parameters, namely the brightness normalisation and the
start and end points on the path.  The latter two are equivalent to
considering the location of the caustic with respect to the starting
point and the velocity component of the source transverse to the
caustic (that is, $v_p$).  The orientation of the source track is
another nuisance parameter.  For a pure fold, changing the orientation
of the source track is equivalent to changing $v_p$ and the
orientation of the source (see Figure~\ref{fig:infinite_fold}).  Since
the latter two parameters are already accounted for, we do not include
the orientation as a separate parameter.  Since the caustic is not a
perfect fold, disregarding the orientation of the source track will
introduce some systematic error.
